Thermodynamic response functions in a cell fluid model

### 2024-07-24 main_morse_response_functions.tex

%**************
\usepackage{graphicx}
%**************

@@

	\section{The equation of state}
	The equation of state obtained in~\cite{KozlovskiiDobush2020} reads
	\begin{equation}
		\label{eq:eos}
		Pv\beta = E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4.
	\end{equation}

	[EXPLICIT EXPRESSIONS FOR QUANTITIES ENTERING THE EQUATION OF STATE FOLLOW HERE OR REFERENCE IS MADE TO AN APPENDIX].

@@

	\bibliographystyle{cmpj} % still looking for the best style
	%\bibliography{fluids_general,fluids_cv} % BibTeX / BibLaTeX should be used
	\bibliography{extracted}

>>>>

%**************
%<<<<<<< HEAD
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}    % for "\eqref" macro
%=======
\usepackage{graphicx}
%>>>>>>> 3a31f0b6bd43223c1786eb91b76133393bfa7c2a
%**************

@@

	\section{The equation of state}
	The equation of state obtained in~\cite{KozlovskiiDobush2020} reads
	\begin{equation}
		\label{eq:eos}
		Pv\beta = E_\mu(M, T) + M \bar \rho_0 + \frac{1}{2} \tilde D(0) \bar \rho_0^2 - \frac{a_4}{24} \bar \rho_0^4.
	\end{equation}
	[EXPLICIT EXPRESSIONS FOR QUANTITIES ENTERING THE EQUATION OF STATE FOLLOW HERE OR REFERENCE IS MADE TO AN APPENDIX].
	The latter expression links the pressure $P$, the temperature $T$ ($\beta = 1/T$ is the inverse temperature), the cell's volume $v$ and the effective chemical potential $M$. In general $M$ is a function of the real chemical potential $\mu$:
	\begin{align}\label{chem_pot}
		&	M = \frac{\tilde\mu}{W(0)} + g_1 + n_c \tilde D(0) - \frac{1}{6} \frac{g_3^3}{g_4^2}, \\
		&	\tilde\mu=\mu-\mu^*(1+\tau),
	\end{align}
	here $\mu^*$ is some positive constant, and $\tau$ is the relative temperature $\tau = (T - T_c) / T_c$,
	$T_c$ is the critical temperature. $W(0)$ is what we call an effective interaction potential\footnote{\textbf{explain} what is the effective interaction potential in a few words} at ${\bf k} = 0$:
	\begin{equation}
	W(0) = \Phi^{(r)}(0) \left[ B - 1 + \chi_0 + \tau (\chi_0 + A_\gamma) \right].
	\end{equation}
	Here $\chi_0$ is a constant parameter, the quantities $B$ and $A_\gamma$ reads
	\begin{align} 
		& B = 2 \gamma^3 e^{(1-\gamma)/\alpha},\nonumber \\
		& A_\gamma = A e^{(n_0-\gamma)/\alpha} \left( \gamma / n_0\right)^3.
	\end{align}
	The coefficients $g_n$ are given by the formulas:
	\begin{align}
		& g_0 = \ln T_0, \qquad g_1 = T_1/T_0, \qquad g_2 = T_2/T_0 - g_1^2,  \nonumber \\
		& g_3 = T_3/T_0 - g_1^3 - 3g_1 g_2, \quad \qquad  g_4 = T_4/T_0 - g_1^4 - 6 g_1^2 g_2 - 4 g_1 g_3 - 3 g_2^2,
	\end{align}
	where $T_n(p,\alpha^*)$ are the following special functions
	\begin{equation}
	T_n(p,\alpha^*) = \sum_{m=0}^{\infty} \frac{(\alpha^*)^m}{m!} m^n e^{pm^2}.
	\end{equation}
	Here $\alpha^*=v e^{\beta_c\mu^*}$, and the parameter $p$ has the form
	\begin{equation}
	p = \frac{\beta_c}{2} \Phi^{(r)}(0) [\chi_0 + A_\gamma].
	\end{equation} 
	Note that we denote $\beta_c$ as the inverse critical temperature. Since $p$ fails to be the function of temperature, the coefficients $g_n$ are also temperature-free. The quantity $\tilde D(0)$ which has already appeared in both equations \eqref{eq:eos} and \eqref{chem_pot} is a function of temperature
	\begin{equation}
	\tilde D(0) = g_2 - \frac{1}{2} \frac{g_3^2}{g_4} - \frac{1}{\beta W(0)},
	\end{equation}
	which equals zero at $T=T_c$. This circumstance gives us an expression for determining the critical temperature 
	\begin{equation}
		T_c = \left(g_2 - \frac{1}{2} \frac{g_3^2}{g_4} \right) (B - 1 + \chi_0) \Phi^{(r)}(0).
	\end{equation}    
	The function $E_\mu(M, T)$ from the equation \eqref{eq:eos} is provided by
	\begin{align}
		& E_\mu (M, T) = - \frac{1}{2 N_v} \ln (2\pi \beta W(0)) +  g_0 - \frac{\beta W(0)}{2} \!\! \left( \! \frac{\tilde\mu}{W(0)} \! \right)^{\! 2} \!\!\! - \frac{g_3}{g_4} {M} \! - \frac{g_3^2}{2 g_4^2}  \tilde D(0) - \frac{1}{24} \frac{g_3^4}{g_4^3}. 
	\end{align}
	Note that for all $ \tau> 0 $ there are no restrictions on the value of $ \bar \rho_0 $, which is a function of the temperature and the chemical potential
	\begin{equation}\label{2d18}
	\bar \rho_0 = \left(- \frac{3\bar{M}}{g_4} + \sqrt{Q_t}\right)^{1/3} - \left(  \frac{3\bar{M}}{g_4} + \sqrt{Q_t} \right)^{1/3} \!\!\!\! ,
	\end{equation}
	where
	\begin{equation}
	Q_t = \left(  \frac{2\tilde D(0)}{g_4}\right)^3 + \left( -\frac{3\bar{M}}{g_4}\right)^2, \qquad g_4<0.
	\end{equation}  
	...
	\begin{equation}\label{3d3}
	\bar n = n_g - \bar{M} + \tilde g_2 \gamma_\tau \bar \rho_0,
	\end{equation}
	where
	\begin{equation}\label{3d4}
	n_g = g_1 + n_c \tilde g_2 - \frac{1}{6} g_3^3 / g_4^2.
	\end{equation}
	...

@@

	%\bibliographystyle{cmpj} % still looking for the best style
	\bibliographystyle{elsarticle-num}
	%\bibliographystyle{unsrturl}
	%\bibliography{fluids_general,fluids_cv} % BibTeX / BibLaTeX should be used
	\bibliography{extracted}
